\section{Stakeholders}
Stakeholders for a project focused on creating a pet adoption platform in Vietnam would include a diverse range of individuals, organizations, and groups with an interest in or influence over the project. Here are some key stakeholders:
\begin{itemize}
  \item \textit{Administrator:} The administrator is responsible for managing and overseeing the platform's operations. They have control over user accounts, content moderation, and the overall functionality of the website.
  \item \textit{Pet Adopter:} Pet adopters are individuals looking to provide a loving home to pets available for adoption. They may already own pets or be first-time pet owners. Pet adopters interact with pet owners and adoption agencies through messaging and inquiries about available pets. They can also share their adoption stories and experiences with the platform's community.
  \item \textit{Pet Owner:} Pet owners are individuals who currently own and care for pets, including dogs, cats, or other animals. Or those, for various reasons, have decided to give their pets to new homes. Reasons may include relocation, financial constraints, allergies, or changes in life circumstances.
  \item \textit{Guest:} Guests are individuals who visit the platform without creating an account or logging in. They have limited access to platform features and content. Guests can browse public content, view pet listings, read provided blogs, and explore the platform's resources. They can also choose to create an account to access more features.
  \item \textit{Pet Adoption Agencies and Shelters:} Organizations involved in pet adoption, rescue, and rehoming would benefit from the platform as it could help them find suitable homes for abandoned or rescued animals. They might also contribute content and listings.
  \item \textit{Pet-Related Businesses:} Pet stores, pet food suppliers, grooming salons, veterinary clinics, and other businesses in the pet industry have a stake in the project. They could use the platform to advertise their products and services to a targeted audience.
  \item \textit{Veterinarians:} Veterinarians play a crucial role in pet healthcare. They might use the platform to provide information, answer questions, and offer telehealth services. Their expertise can be valuable to pet owners.
  \item \textit{Investors and Funders:} Individuals or organizations providing funding or investment for the development and scaling of the platform are stakeholders with a financial interest.
\end{itemize}

Understanding and engaging with these stakeholders will be important for the success and sustainability of the project. Each stakeholder group may have different needs, interests, and concerns that should be addressed during the project's planning and execution.
