The “Petopia - Pet Adoption Platform” project is a comprehensive initiative aimed at improving the process of pet adoption. This online platform serves as a bridge, connecting potential pet adopters with animal shelters and rescue groups in Ho Chi Minh City. The primary goal is to streamline the adoption process, making it easier for people to find their perfect pet companion and also creating a hub where pet enthusiasts can access information and gain knowledge about pet care.

The platform provides detailed profiles of each pet available for adoption. This allows potential adopters to gain a thorough understanding of the pet. One of the key features of the platform is its advanced search functionality. Users can search for pets based on various criteria such as breed, size, age, and pictures with the support of AI technology. This feature is designed to help users find a pet that fits their lifestyle and preferences, thereby increasing the rate of successful adoption.

In addition, the platform also offers a wealth of resources for pet lovers. These resources cover a wide range of topics, from the adoption process itself to pet care tips and advice. The aim is to equip new pet owners with the knowledge they need to provide their new pets with a loving and caring home.

In conclusion, by applying the knowledge of programming and software engineering, this capstone project hopes to create a solution that benefits both animals in need and potential pet owners. It aims to reduce the number of animals in shelters and rescue groups by increasing the rate of successful adoptions. At the same time, it seeks to bring joy and companionship to families and individuals looking to adopt a pet.
