\chapter{SYSTEM TESTING}

With the completion of system implementation, our focus now shift towards 
ensuring the robustness and functionality of the system through testing. 
This section presents the systematic approach taken for system testing, 
including end-to-end testing and API testing, to validate the functionality 
and performance of the implemented system

\section{End to end testing}


\section{API testing}
This chapter delves into testing the website's API for functionality using 
Postman. Postman's versatile features were utilized to conduct thorough 
assessments of the API endpoints, ensuring data integrity and performance 
across diverse scenarios. Through rigorous experimentation and analysis, 
Postman facilitated the establishment of a robust validation framework, 
affirming the reliability of the website's API under different conditions.

\subsection{API endpoints}
The website's API endpoints were meticulously tested to ensure their
functionality and performance across various scenarios. The API endpoints
were designed to handle different types of requests, including GET, POST,
PUT, and DELETE, to interact with the database and retrieve or modify
data. By testing these endpoints, we could verify the accuracy and
reliability of the API, ensuring that it could handle different types of
requests and return the expected results.

\subsection{API testing with Postman}
Postman was used to test the website's API endpoints, leveraging its
versatile features to conduct comprehensive assessments. Postman's
user-friendly interface and powerful testing capabilities enabled us to
create test cases, execute requests, and analyze responses efficiently.
By defining test scripts and assertions, we could validate the API
endpoints' functionality and performance, ensuring that they met the
specified requirements.

\subsection{API testing scenarios}
Various testing scenarios were explored to evaluate the website's API
endpoints thoroughly. These scenarios included testing different types of
requests, handling error conditions, and assessing the API's performance
under load. By simulating real-world usage scenarios and edge cases, we
could identify potential issues and validate the API's behavior in
different situations. This comprehensive testing approach helped ensure
the reliability and robustness of the website's API, enhancing its overall
quality and performance. 

Here is all the test cases for the API endpoints. All the API endpoints
here have average response time of 734ms. The test cases are divided into:


\input{Tables/ApiTesting/AdoptionTable.tex}

\input{Tables/ApiTesting/AuthenticationTable.tex}

\input{Tables/ApiTesting/BlogTable.tex}

\input{Tables/ApiTesting/CommentTable.tex}

\input{Tables/ApiTesting/Location.tex}

\input{Tables/ApiTesting/Notification.tex}

\input{Tables/ApiTesting/Payment.tex}

\input{Tables/ApiTesting/PetTable.tex}

\input{Tables/ApiTesting/ReportTable.tex}

\input{Tables/ApiTesting/UserTable.tex}

\section{Responsive testing}
Responsive testing is a crucial aspect of web development, ensuring that
websites are accessible and user-friendly across different devices and
screen sizes. By testing the website's responsiveness, we could verify
that it displayed correctly on various devices, including desktops,
laptops, tablets, and smartphones. This testing process involved
evaluating the website's layout, design, and functionality on different
devices, ensuring a consistent and seamless user experience. By
identifying and addressing any responsiveness issues, we could enhance
the website's usability and accessibility, catering to a broader audience
and improving user satisfaction.



