\chapter{CONCLUSION}

In conclusion, we have successfully completed about 90\% of our initial project goals. Our developed system establishes a platform that connects pet shelters, rescues, pet owners, and potential adopters. It simplifies the adoption process by enabling users to submit adoption applications online and finalize the adoption process digitally.

Furthermore, the software system enhances the efficiency of SGT administrators in managing their operations. It offers tools for handling pet records, monitoring adoptions, and tracking system usage. Additionally, it assists shelters, rescues, and other businesses in promoting their services.

The system also includes a blog function for SGT and website partners to write news and tips about pets. This function includes an advertisement feature with online payment options to promote a blog, providing SGT with a new source of income to support their organization.

Despite these accomplishments, we encountered some challenges that prevented us from fully developing our ideal system. Specifically, we have not yet developed the messaging and personalized pet recommendation features as intended. This shortfall is primarily due to underestimating the time required to integrate AI pet recognition into our system, which extended our development timeline and necessitated cutting less critical features.

For future development, our plans include:

\begin{itemize}
    \item Completing the messaging feature to allow users to communicate with each other and with SGT administrators.
    \item Implementing the personalized pet recommendation feature to help users find pets that match their preferences.
    \item Enhancing the system's security by implementing additional security measures to protect user data.
    \item Further improving the AI pet recognition system to recognize more species of animals beyond just dogs and cats.
    \item Based on the advantages of our application's layered design pattern, we plan to create a mobile app since we only need to modify the presentation layer.
\end{itemize}

Overall, our system has laid a strong foundation for bridging the gap in pet adoption processes, and with continued development, we aim to enhance its functionality and accessibility further.