\begin{longtblr}[
    caption = {Use Case: Adopt pets},
    label = {tblr:adopt_pets_use_case},
  ]{
    vline{1-12} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[3,l] X[7, l]},
  }
  \textbf{Use-case name} & \textbf{Adopt Pets} \\
  \textbf{Actors} & {
    User as Pet Adopter and Pet Owner
  } \\
  \textbf{Preconditions} & {
    1. Users logged successfully into the system.
    \\2. Users find pet profiles successfully.
  } \\
  \textbf{Postconditions} & {
    Pet owners receive and handle the submitted application successfully.
  } \\
  \textbf{Triggers} & {
    The adopters choose a pet profile and want to adopt.
  } \\
  \textbf{Normal flow} & {
    1. Pet adopters click the adopt button on a pet profile. The system displays a form screen of required information.
    \\2. Pet adopters fill required information and apply.
    \\3. Pet Owners receive and view the applications.
    \\4. Pet Owners accept the applications.
    \\5. The system updates the pet profile status and notifies the pet adopter of the results of the applications.
  } \\
  \textbf{Alternative flows} & {
    Alternative flow 1, from step 3:
    \\3. Pet adopters cancel their applications before Pet Owners accept them.
    \\Alternative flow 2, from steps 4 to 5:
    \\4. Pet Owners decline the applications.
    \\5. The system notifies pet adopters of the results of the applications.
  } \\
  \textbf{Exceptions} & {
    1. The pets already have new owners during the adoption process.
\\2. Pet adopters already sent a form before.

  } \\
\end{longtblr}
