\begin{longtblr}[
    caption = {Functional Requirements},
    label = {tblr:func_req},
  ]{
    vline{1-3} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[2,l] X[5, l]},
  }
  \textbf{Group}                                & \textbf{Requirements}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      &  &  \\
  \textbf{Authentication and authorization}     & {
    -~~~~~~~
    Users can create new accounts by providing personal information.
    \\-~~~~~~~
    Users can log into the system using Google accounts.
    \\-~~~~~~~
    Users can log into the system by
    providing a registered email and password.
    \\-~~~~~~~
    Users can send applications to the system to update their accounts to
    Organization accounts.
    \\-~~~~~~~
    Admins can verify Organizations’ registration and upgrade users’
    accounts.
    \\-~~~~~~~
    Users can reset or recover their account passwords.
    }                                                          &  &  \\
  \textbf{Pet profile management}               & {
    -~~~~~~~
    Users can create pet profiles by giving details such as name, species,
    breed, age, color, health status, sterilization status, pictures, and videos
    of pets.
    \\-~~~~~~~
    Users can provide information about breed, species, and color by
    uploading pets’ pictures.
    \\-~~~~~~~
    Pet photos and text inputs must be sensitive-validated before
    uploading.
    \\-~~~~~~~
    Users can edit their pet profiles.
    \\-~~~~~~~
    Users can publish, hide, or remove their pet profiles.
    \\-~~~~~~~
    Admins can remove or hide any pet profiles of the system.
    } &  &  \\
  \textbf{Pet profile filter and view}          & {
    -~~~~~~~
    Users can search for pets by providing filtering options such as name,
    species, breed, age, color, health status, and sterilization status.
    \\-~~~~~~~
    Users can search for pets by providing pets’ pictures.
    \\-~~~~~~~
    Users can view pet profiles with detailed information such as name,
    species, breed, age, color, health status, sterilization status, pictures,
    and videos of pets
    }                                                                                                                                                                &  &  \\
  \textbf{Pet adoption}                         & {
    -~~~~~~~
    Users can submit applications to adopt pets on the system.
    \\-~~~~~~~
    Users can view, decline, or accept adoption applications sent to their
    pets.
    }                                                                                                                                                                                                                                                                                                                                                                                                                &  &  \\
  \textbf{User interaction and engagement}      & {-~~~~~~~
  Pet
  Adopters can send messages to Pet Owners, Organizations, and Admins.
  \\-~~~~~~~PetAdopters have to update their pets’ status every seven days[1]~ from the date they received the petsby uploading posts in the adopt status section of the pet profile.\\-~~~~~~~
  Pet
  Adopters can set their posts public for all users or just Admins, and Pet
  Owners.
  \\-~~~~~~~
  Admins
  and Pet Owners can view and interact with posts from Pet Adopters.
  \\-~ ~ ~ ~ All users of the system can view and interact
  with posts from Pet Adopters if the posts are public.~ ~ ~~}        &  &  \\
  \textbf{Blog management}                      & {
    -~~~~~~~
    Admins and Organizations can create and publish blogs.
    \\-~~~~~~~
    Organizations can apply advertisements on their blogs.
    \\-~~~~~~~
    Organizations can edit or remove their blogs.
    \\-~~~~~~~
    Admins can hide or remove any blogs of the system.
    }                                                                                                                                                                                                                                                                                                             &  &  \\
  \textbf{Advertisement and payment}            & {
    -~~~~~~~
    Organizations can choose advertisement duration with different prices.
    \\-~~~~~~~
    Organizations can pay advertisement fees through an online banking
    service.
    \\-~~~~~~~
    Admins can receive advertisement fees through an online banking
    service.
    \\-~~~~~~~
    System provides admins and organizations information like payment
    status and invoices.
    }                                                                                                                                                                                                   &  &  \\
  \textbf{Notifications}                        & {
    -~~~~~~~
    Users can receive notifications on new pet adoption applications.
    \\-~~~~~~~
    Users can receive notifications on new pets’ status posts uploaded.
    \\-~~~~~~~
    Users can receive notifications on new pet profiles matching their
    criteria.
    }                                                                                                                                                                                                                                                                                                                      &  &  \\
  \textbf{System statistics for administrators} & -~~~~~~~
    Admins can get statistics about systems usages, such as the number of
    pet profiles, adopted pets; number of users and Organizations; number of
    blogs, and the total amount of advertisement fee.                                                                                                                                                                                                                                                                                                                                                                            &  &  
\end{longtblr}
