\begin{longtblr}[
    caption = {Use Case: Log in},
    label = {tblr:login_use_case},
  ]{
    vline{1-16} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[3,l] X[7, l]},
  }
  \textbf{Use-case name} & \textbf{Log in} \\
  \textbf{Actors} & {
    General User, Google OAuth Service
  } \\
  \textbf{Preconditions} & {
    User at login page
  } \\
  \textbf{Postconditions} & {
    Users log in successfully and can access authorized features.
  } \\
  \textbf{Triggers} & {
    1. Users access any authorized features of the system without being authorized.
    \\2. Users want to log in to the system.
  } \\
  \textbf{Normal flow} & {
    1. Users click on the login button of the system. The system displays a login form screen.
    \\2. User provides authentication information including email and password.
    \\3. The system verifies the authentication information.
    \\4. System grants access permission to users.
  } \\
  \textbf{Alternative flows} & {
    Alternative flow 1, at step 1:
    \\1. Users access any authorized features of the system without being authorized.
    \\Alternative flow 2:
    \\1. Users choose the option of login with a Google account. The system displays a Google login form screen.
    \\2. Users provide Google authentication information.
    \\3. Google Auth service verifies the authentication information and generates access tokens.
    \\4. System validates access token and grants access permission to users.
  } \\
  \textbf{Exceptions} & {
    1. Users input the wrong authentication information.
    \\2. Users do not have an account.
    \\3. Users do not have a Google account.
  } \\
\end{longtblr}
