\begin{longtblr}[
    caption = {Use Case: Manage pet profile},
    label = {tblr:manage_pet_profile_use_case},
  ]{
    vline{1-14} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[3,l] X[7, l]},
  }
  \textbf{Use-case name}     & \textbf{Manage pet profile} \\
  \textbf{Actors}            & {
      User, Pet Recognization Service.
  }                                                        \\
  \textbf{Preconditions}     & {
      Users logged successfully into the system.
  }                                                        \\
  \textbf{Postconditions}    & {
      Users create and edit their pet profiles successfully.
  }                                                        \\
  \textbf{Triggers}          & {
      Users access the pet profile management section of the system.
  }                                                        \\
  \textbf{Normal flow}       & {
      1. Users click on the add profiles button of the system. The system displays a form screen of a pet profile.
  \\2. Users input their pet images. Pet Recognition Service automatically fills breed and color fields.
  \\3. Users fill in the remaining fields and submit.
  \\4. The system verifies submitted information using the Content Moderation service.
  \\5. The system creates new pet profiles and notifies the users.
  }                                                        \\
  \textbf{Alternative flows} & {
      Alternative flow 1, from step 2 to step 3:
  \\2. Users input the forms manually.
  \\Alternative flow 2, at step 3:
  \\3. Users edit input fields generated by Pet Recognization Service and submit.
  \\Alternative flow 3:
  \\1. Users choose their available pet profiles and click on the edit button. The system displays a form screen of pet profiles.
  \\2. Users edit and submit their pet information.
  \\3. The system updates the pet profiles and notifies the users.
  \\Alternative of flow 3, from step 2 of alternative flow 2:
  \\2. Users choose to remove their pet profiles. The system asks for confirmation.
  \\3. Users confirm removing pet profiles. The system deletes pet profiles and notifies users.
  }                                                        \\
  \textbf{Exceptions}        & {
      Pet Recognization Service cannot detect and fill in pet information.
  }                                                        \\
\end{longtblr}
