\begin{longtblr}[
    caption = {Non-Functional Requirements},
    label = {tblr:non_func_req},
  ]{
    vline{1-3} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[2,l] X[5, l]},
  }
  \textbf{Group}         & \textbf{Requirements} \\
  \textbf{Performance}   & {
      -~~~~~~~
      The system should respond to pages loading in under 2 seconds.
  \\-~~~~~~~
      The period for payment transaction (from starting the transaction to receiving the result notification) period is at most 10 seconds.
  \\-~~~~~~~
      The period for pet profiles filtering is at most 2 seconds.
  \\-~~~~~~~
      Every API call should have a response time of less than 1 second (excluding payment and pet filtering APIs).
  }                                              \\
  \textbf{Localization}  & {
      -~~~~~~~
      All the system data and user inputs of time are in the format of "dd/mm/yyyy” or “hh:mm - dd/mm/yyyy”.
  \\-~~~~~~~
      All the system data and user inputs of address are in the format of “street, ward, district, city”.
  \\-~~~~~~~
      The language used in the system is Vietnamese.
  }                                              \\
  \textbf{Security}      & {
      -~~~~~~~
      The system data (such as email, password, and personal information) must be encrypted before being stored in the database.
  \\-~~~~~~~
      User unauthorized access to system features and data must be prevented using authorization with JWT tokens.
  \\-~~~~~~~
      System uses secured data transmission over the internet (TLS, HTTPS).
  \\-~~~~~~~
      System components (API servers, database servers, file storage,..) must be protected from external accesses.
  \\-~~~~~~~
      System must have at least one backup database that is kept synchronized for potential problems with the main database.
  \\-~~~~~~~
      User register requests must be challenged by a reCAPTCHA service.
  }                                              \\
  \textbf{Compatibility} & {
      -~~~~~~~
      The web application of the system functions correctly on popular web browsers, such as Chrome, Safari, and Edge.
  \\-~~~~~~~
      The web application of the system supports responsiveness and works well on various devices and screen sizes (smartphones, tablets, desktops).
  }                                              \\
  \textbf{Reliability}   & {
      -~~~~~~~
      The system must perform without failure in 95 percent of use cases during a month.
  \\-~~~~~~~
      Run smoothly when 1000 requests access in 30 seconds.
  }                                              \\
  \textbf{Usability}     & {
      -~~~~~~~
      The maximum amount of time for new users to get familiar with the web application of the system is 5 minutes.
  \\-~~~~~~~
      The steps to give and adopt a pet must be short and straightforward.
  }                                              \\
  \textbf{Scalability}   & {
      -~~~~~~~
      The backend components of the system can be reused to build a mobile application in the future.
  \\-~~~~~~~
      The design patterns of the systems must be able to further implement new features in the future.
  }                                              \\
\end{longtblr}
