\begin{longtblr}[
    caption = {Use Case: Make payment},
    label = {tblr:make_payment_use_case},
  ]{
    vline{1-10} = {-}{},
    hline{-} = {1-2}{},
    colspec={X[3,l] X[7, l]},
  }
  \textbf{Use-case name} & \textbf{Make payment} \\
  \textbf{Actors} & {
    Organization, Admin, Payment service
  } \\
  \textbf{Preconditions} & {
    Organizations create a blog successfully.
  } \\
  \textbf{Postconditions} & {
    1. Organizations have blogs that have the correct advertisement duration.
    \\2. Admins receive payment from organizations.
  } \\
  \textbf{Triggers} & {
    Organizations apply advertisements on their blogs.
  } \\
  \textbf{Normal flow} & {
    1. The system shows all advertisement types with their periods.
    \\2. Users choose a type of advertisement. The system shows the payment invoice.
    \\3. Users confirm all the payment policies and finish the payments.
    \\4. Payment service processes the transactions.
    \\5. Admins receive the payments from the organizations.
    \\6. System notifies organizations and admins of successful payments.
  } \\
  \textbf{Alternative flows} & {
    Alternative flow 1, at step 3:
    \\3. Users can refuse the payment policies and stop the payments.
    \\Alternative flow 2, from step 4:
    \\4. Payment service processes the transactions and gets errors.
    \\5. System notifies organizations of failed payments.
  } \\
  \textbf{Exceptions} & {
    1. Organizations do not use the supported payment service.
    \\2. The balances in the accounts of organizations are not enough.
    \\3. Internal errors in the payment service occur.
  } \\
\end{longtblr}
