\begin{longtblr}[
    caption = {API Testing for User Function},
    label = {tblr:api_user},
  ]{
    hlines, vlines,
    colspec = {X[0.6,l] X[2.5,l] X[3,l] X[4,l] X[0.8,l] X[1.5,l]},
    row{1} = {font=\bfseries},
  }
    Id & Api & Testcase & Expected result & Result & \SetCell[c=1]{c}Response time \\
    \SetCell[r=2]{c}1 & \SetCell[r=2]{c}GET - /User/CurrentUser & 1. Unauthorized & Error code 401 with message "Unauthorized". & Pass & \SetCell[r=2]{c}694ms \\
    & & 2. Authorized & Status 200. & Pass & \\
    \SetCell[r=2]{c}2 & \SetCell[r=2]{c}GET - /User/CurrentUserCore & 1. Unauthorized & Error code 401 with message "Unauthorized". & Pass & \SetCell[r=2]{c}884ms \\
    & & 2. Authorized & Status 200. & Pass & \\
    \SetCell[r=2]{c}3 & \SetCell[r=2]{c}GET - /User/OtherUser & 1. Unauthorized & Status 200. & Pass & \SetCell[r=2]{c}664ms \\
    & & 2. Authorized & Status 200. & Pass & \\
    \SetCell[r=3]{c}4 & \SetCell[r=3]{c}POST - /User/ForgotPassword & 1. Wrong login type & Error code 10006 with message "Wrong login type". & Pass & \SetCell[r=3]{c} \\
    & & 2. Wrong email & Error code 10000 with message "Provided email is not correct" & Pass & \\
    & & 3. Correct email & Status 200. & Pass & \\
    \SetCell[r=3]{c}5 & \SetCell[r=3]{c}PUT - /User & 1. Unauthorized & Error code 401 with message "Unauthorized". & Pass & \SetCell[r=3]{c}654ms \\
    & & 2. Empty body & Error code 400 with corresponding empty fields & Pass & \\
    & & 3. Correct body & Status 200 & Pass & \\
    \SetCell[r=3]{c}6 & \SetCell[r=3]{c}PUT - /User/UpdateAvatar & 1. Unauthorized & Error code 401 with message "Unauthorized". & Pass & \SetCell[r=3]{c}670ms \\
    & & 2. Correct body & Status 200 & Pass & \\
    & & 3. Empty image & Error code 400 with message "Image cannot be empty" & Pass & \\
    \SetCell[r=3]{c}7 & \SetCell[r=3]{c}POST - /User/UpgradeAccount & 1. Unauthorized & Error code 401 with message "Unauthorized". & Pass & \SetCell[r=3]{c}593ms \\
    & & 2. Has not applied & Status 200 & Pass & \\
    & & 3. Has applied & Status 200 with message False & Pass & \\
  \end{longtblr}